---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

suppressPackageStartupMessages({
  library(dplyr)
  library(ggplot2)
})

```
# poissoned

<!-- badges: start -->
![](https://img.shields.io/badge/cool-useless-green.svg)
[![CRAN](https://www.r-pkg.org/badges/version/poissoned)](https://CRAN.R-project.org/package=poissoned)
[![R-CMD-check](https://github.com/coolbutuseless/poissoned/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/coolbutuseless/poissoned/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

`poissoned` is an Rstats implementation of the poisson disk sampling algorithm from 
[Bridson's paper - Fast Poisson Disk Sampling in Arbitrary Dimensions](https://www.cs.ubc.ca/~rbridson/docs/bridson-siggraph07-poissondisk.pdf)


## Multi-dimensional poisson disc sampling


## Installation

You can install from [GitHub](https://github.com/coolbutuseless/poissoned) with:

``` r
# install.packages("devtools")
devtools::install_github("coolbutuseless/poissoned")
```
## Basic Usage



```{r example}
library(poissoned)

set.seed(1)
points <- poissoned::poisson_disc(ncols = 50, nrows = 35, cell_size = 10, verbose = TRUE)

ggplot(points) +
  geom_point(aes(x, y)) +
  theme_bw() +
  coord_fixed() +
  theme(
    panel.grid = element_blank(),
    axis.title = element_blank()
  ) 
```


# Tileability

The points generated from `poissoned::poisson_disc()` are tileable in that there 
should be minimal artifacts at the joins.

In the graph below, the initial set of points (highlighted in blue) was manually replicated
and offset eight times.

```{r echo = FALSE}
ncols     <- 15
nrows     <- 10
cell_size <- 10


set.seed(2)
points <- poissoned::poisson_disc(ncols = ncols, nrows = nrows)

width     <- ncols * cell_size
height    <- nrows * cell_size

off <- expand.grid(
  xoff = -1:1 * width,
  yoff = -1:1 * height
)

tiled_points <- merge(points, off) %>%
  as.tbl() %>%
  mutate(
    x = x + xoff,
    y = y + yoff
  )



ggplot(tiled_points) +
  geom_rect(xmin = 0, xmax = width, ymin = 0, ymax = height, fill = 'lightblue') +
  geom_point(aes(x, y), size = 2) +
  theme_bw() +
  coord_fixed() +
  theme(
    panel.grid = element_blank(),
    axis.title = element_blank()
  ) +
  labs(title = "The initial point set (blue highlight) is repeated and tiled (seamlessly!)")
```




# Tileability - details

Tileability is achieved by copying edge points to outside the opposite edge - this
simulates a toroidal coordinate system such that the canvas wraps around on itself.

These boundary points are retrievable by setting `keep_boundary = TRUE`.  

In the following plot, the dashed line indicates the limits of the point set, 
and the blue points are translated points copied from the opposite edge.


```{r echo = FALSE}
set.seed(1)
```

```{r tileability_details}
points <- poissoned::poisson_disc(ncols = 15, nrows = 10, cell_size = 20, 
                                  keep_boundary = TRUE, verbose = TRUE)

ggplot(points) +
  geom_rect(xmin = 0, xmax = 300, ymin = 0, ymax = 200, fill = NA, colour = '#a0a0a0', linetype = 2) + 
  geom_point(aes(x, y, colour = boundary), size = 5) +
  theme_void() +
  coord_fixed() +
  theme(legend.position = 'none') +
  labs(title = "Blue points are points used to enforce a boundary condition to ensure \noutput point set is tileable")
```





# Point discovery order

New points are generated through an iterative process. `poisson_disc()` can
return the order in which points were generated using the `keep_idx` argument.

It is also possible to pass in the seed point to initialise the process. If a
seed point is not given, then a random point will be chosen.


```{r echo = FALSE}
set.seed(1)
```

```{r discovery_order}
points <- poissoned::poisson_disc(ncols = 120, nrows = 80, cell_size = 10, 
                                  xinit = 600, yinit = 400,
                                  keep_idx = TRUE, verbose = TRUE)

nrow(points)

ggplot(points) +
  geom_point(aes(x, y, colour = idx)) +
  theme_void() +
  coord_fixed() +
  theme(legend.position = 'none') +
  scale_color_viridis_c() +
  labs(title = "Seed point at centre. Points coloured by discovery order.")
```





```{r echo = FALSE, eval = FALSE}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Generate an animation of the points being found
#
# 1. Create points
# 2. Render a bunch of ggplots - each showing more of the points
# 3. ffmpeg -r 60 -f image2 -i %05d.png -vcodec libx264 -crf 25  -pix_fmt yuv420p -s 800x500 ../test4000.mp4
#
# Note: gganimate barfed when trying to render, so I switched to this manual process.
#
# ffmpeg info from:
# http://hamelot.io/visualization/using-ffmpeg-to-convert-a-set-of-images-into-a-video/
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

suppressPackageStartupMessages({
  library(magrittr)
  library(dplyr)
  library(ggplot2)
  library(furrr)
})


plan(multiprocess)

width  <- 150 * 0.9
height <- 100 * 0.9

set.seed(1)
points <- poisson_disc(ncols = width, nrows = height, cell_size = 2,
                       xinit = width, yinit = height,
                       keep_boundary = FALSE, verbose = TRUE)

points <- points %>% arrange(idx)
nrow(points)


create_plot <- function(i) {
  plot_df <- points %>% slice(seq(i))
  
  p <- ggplot(plot_df) +
    geom_point(aes(x, y), size = 0.2) +
    theme_void() +
    coord_fixed() +
    theme(legend.position = 'none') +
    xlim(0, width  * 2) +
    ylim(0, height * 2)
  
  filename <- sprintf("working/%05i.png", i)
  ggsave(filename, plot = p, width = 4, height = 3.2)
  
  i
}

zz <- (seq_len(max(points$idx))) %>%
  furrr::future_map_int(create_plot)
```




```{r echo = FALSE, eval = FALSE}
set.seed(1)

# animated palette
points <- poissoned::poisson_disc(ncols = 60, nrows = 40, cell_size = 10, 
                                  xinit = 300, yinit = 200,
                                  keep_idx = TRUE, verbose = TRUE)

dir.create("cycle", showWarnings = FALSE)

N <- max(points$idx)
points$idx <- N - points$idx

offsets <- as.integer(seq(1, N, length.out = 120))

offset <- offsets[1]
for (offset in offsets) {

points$idx2 <- (points$idx + offset) %% N
p <- ggplot(points) +
  geom_point(aes(x, y, colour = idx2)) +
  theme_void() +
  coord_fixed() +
  theme(legend.position = 'none') +
  scale_color_viridis_c() 


filename <- sprintf("cycle/c%04i.png", offset)
ggsave(filename, p, width = 3, height = 2)
}
```


















