---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

suppressPackageStartupMessages({
  library(dplyr)
  library(ggplot2)
})

```
# poissoned

<!-- badges: start -->
![](https://img.shields.io/badge/cool-useless-green.svg)
[![CRAN](https://www.r-pkg.org/badges/version/poissoned)](https://CRAN.R-project.org/package=poissoned)
[![R-CMD-check](https://github.com/coolbutuseless/poissoned/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/coolbutuseless/poissoned/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

`poissoned` is an Rstats implementation of the poisson disk sampling algorithm from 
[Bridson's paper - Fast Poisson Disk Sampling in Arbitrary Dimensions](https://www.cs.ubc.ca/~rbridson/docs/bridson-siggraph07-poissondisk.pdf)


## Multi-dimensional poisson disc sampling


## Installation

You can install from [GitHub](https://github.com/coolbutuseless/poissoned) with:

``` r
# install.packages("devtools")
devtools::install_github("coolbutuseless/poissoned")
```
## Basic Usage



```{r example}
library(poissoned)

set.seed(1)
points <- poissoned::poisson_disc(ncols = 50, nrows = 35, cell_size = 10, verbose = TRUE)

ggplot(points) +
  geom_point(aes(x, y)) +
  theme_bw() +
  coord_fixed() +
  theme(
    panel.grid = element_blank(),
    axis.title = element_blank()
  ) 
```




# Point discovery order

New points are generated through an iterative process. `poisson_disc()` can
return the order in which points were generated using the `keep_idx` argument.

It is also possible to pass in the seed point to initialise the process. If a
seed point is not given, then a random point will be chosen.


```{r echo = FALSE}
set.seed(1)
```

```{r discovery_order}
points <- poissoned::poisson_disc(ncols = 120, nrows = 80, cell_size = 10, 
                                  xinit = 600, yinit = 400,
                                  keep_idx = TRUE, verbose = TRUE)

nrow(points)

ggplot(points) +
  geom_point(aes(x, y, colour = idx)) +
  theme_void() +
  coord_fixed() +
  theme(legend.position = 'none') +
  scale_color_viridis_c() +
  labs(title = "Seed point at centre. Points coloured by discovery order.")
```





```{r echo = FALSE, eval = FALSE}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Generate an animation of the points being found
#
# 1. Create points
# 2. Render a bunch of ggplots - each showing more of the points
# 3. ffmpeg -r 60 -f image2 -i %05d.png -vcodec libx264 -crf 25  -pix_fmt yuv420p -s 800x500 ../test4000.mp4
#
# Note: gganimate barfed when trying to render, so I switched to this manual process.
#
# ffmpeg info from:
# http://hamelot.io/visualization/using-ffmpeg-to-convert-a-set-of-images-into-a-video/
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

suppressPackageStartupMessages({
  library(magrittr)
  library(dplyr)
  library(ggplot2)
  library(furrr)
})


plan(multiprocess)

width  <- 150 * 0.9
height <- 100 * 0.9

set.seed(1)
points <- poisson_disc(ncols = width, nrows = height, cell_size = 2,
                       xinit = width, yinit = height,
                       verbose = TRUE)

points <- points %>% arrange(idx)
nrow(points)


create_plot <- function(i) {
  plot_df <- points %>% slice(seq(i))
  
  p <- ggplot(plot_df) +
    geom_point(aes(x, y), size = 0.2) +
    theme_void() +
    coord_fixed() +
    theme(legend.position = 'none') +
    xlim(0, width  * 2) +
    ylim(0, height * 2)
  
  filename <- sprintf("working/%05i.png", i)
  ggsave(filename, plot = p, width = 4, height = 3.2)
  
  i
}

zz <- (seq_len(max(points$idx))) %>%
  furrr::future_map_int(create_plot)
```




```{r echo = FALSE, eval = FALSE}
set.seed(1)

# animated palette
points <- poissoned::poisson_disc(ncols = 60, nrows = 40, cell_size = 10, 
                                  xinit = 300, yinit = 200,
                                  keep_idx = TRUE, verbose = TRUE)

dir.create("cycle", showWarnings = FALSE)

N <- max(points$idx)
points$idx <- N - points$idx

offsets <- as.integer(seq(1, N, length.out = 120))

offset <- offsets[1]
for (offset in offsets) {

points$idx2 <- (points$idx + offset) %% N
p <- ggplot(points) +
  geom_point(aes(x, y, colour = idx2)) +
  theme_void() +
  coord_fixed() +
  theme(legend.position = 'none') +
  scale_color_viridis_c() 


filename <- sprintf("cycle/c%04i.png", offset)
ggsave(filename, p, width = 3, height = 2)
}
```


















